### 2014-10-28 ThesisJo/derivations.tex
la2pdf commit - 2014:10:28	14:33:53	(Tue28.Oct)

\floatbox{table}[\linewidth][\FBheight][t]{%
\caption{Symbol description}}{%
\begin{tabular}[c]{c c l}\hline
\rowcolor{tabBlue}\bf Symbol & \bf Unit & \bf Description \\\hline
$p$ & Pa = N/m$^2$ & Pressure \\
$\rho$ & kg/m$^3$ & Density \\
$S$ &  & Entropy \\
$\vec v$ & m/s & Mass velocity \\
$\dot m$ & kg/s & Mass flow
\end{tabular}}

@@

We begin by defining the mass flow in and out of a volumetric element $dV = dx dy dz$:

\begin{align}
\dot m_\text{in} = \rho\,\v\,dV \qquad\qquad \text{and} \qquad\qquad \dot m_\text{out} = \rho\,\v\,dV + 
\end{align}

>>>>

\floatbox{table}[\linewidth][\FBheight][t]{%
\caption{Symbol description}}{%
\begin{tabular}[c]{c c l}\hline
\rowcolor{tabBlue}\bf Symbol & \bf Unit & \bf Description \\\hline
$p$ & Pa = N/m$^2$ & Pressure \\
$\rho$ & kg/m$^3$ & Density \\
$S$ & Nm/K & Entropy \\
$\vec v$ & m/s & Mass velocity \\
$\dot m$ & kg/s & Mass flow
\end{tabular}}

@@

We begin by defining the net mass flow in and out of a volumetric element $dV = dx dy dz$:

\begin{align}
\dot m_\text{net} = \Big(\frac{\partial \rho\,\v}{\partial x} + \frac{\partial \rho\,\v}{\partial y} + \frac{\partial \rho\,\v}{\partial z} \Big) dV = \nabla \cdot (\rho\v)\, dV
\end{align}
